---
title: Nakuru Communities Boreholes Inventory
output: 
  flexdashboard::flex_dashboard:
    orientation: column
    vertical_layout: fill
    theme: flatly
    #runtime: shiny
---


```{r setup, include=FALSE}
library(flexdashboard)
library(highcharter)
library(tidyverse)
library(maps)
library(htmlwidgets)
library(leaflet)
library(echarts4r)
library(dplyr)
library(DT)
library(mapview)
library(sf)
library(sp)
library(janitor)
```


# {Mapped Boreholes & Map}
```{r}
  
```


```{r read}
Data4 <- read_csv("F:/Folder E/Nakuru WaterWax/Unicef Project/Data Using R/Borehole Data in Flex dashboard/Data4.csv")

Data4$Longitude <- as.numeric(Data4$Longitude)
Data4$Latitude <- as.numeric(Data4$Latitude)

data.sp <- SpatialPointsDataFrame(Data4[,c(3,4)], Data4[,-c(3,4)])




```



Row {data-width=2300}
-----------------------------------------------------------------------

### Mapped Boreholes Per Sub-County

```{r}


Data4 %>% 
  group_by(Sub_Counties)%>% 
  summarise(Number=n()) %>% 
  arrange(-Number) %>% # indicate - to arrange from big to small
  hchart(
    'bar', hcaes(x=Sub_Counties, y=Number),
    showInLegend=F,
    maxSize = "25%",
    dataLabels = list(enabled = T, format = '{point.y: .0f} ')) %>% 
  hc_title(
    text='Mapped Communities Boreholes',
    style = list(fontWeight = "bold", fontSize = "15px"),
    align = "center") %>% 
  hc_tooltip(sort = TRUE, table = TRUE) %>% 
  #hc_add_theme(hc_theme_darkunica())%>% 
  hc_add_theme(hc_theme_flat()) %>% 
  hc_yAxis(title=list(text='Number' )) %>% 
  hc_xAxis(title=list(text='Nakuru Sub-Counties'))

```

Row {data-width=2300}
--------------------------------------------------------------------

### Map of the Mapped Boreholes

```{r}

```



```{r}
leaflet() %>%
  
addProviderTiles("Esri") %>%
  setView(lng = 36.058758, lat= -0.427551, zoom=9) %>%
 addScaleBar(position='bottomleft') %>% 
  addMeasure() %>% 
  addMarkers(data=Data4, lng = ~Longitude,
   lat = ~Latitude,
   popup = ~Borehole_Name, clusterOptions = markerClusterOptions()) 

```


# {Production, Operation & Population }


Row {data-height=400}
--------------------------------------------------------------------

### Total Sub-County Production

```{r}
 
Data4 %>% 
  group_by(Sub_Counties)%>%
  summarise(Total_Yield=sum(Yield))%>%
  arrange(Total_Yield ) %>% # indicate - to arrange from big to small
  hchart(
    'column', hcaes(x=Sub_Counties, y=Total_Yield),
    showInLegend=F,
    maxSize = "25%",
    dataLabels = list(enabled = T, format = '{point.y: .0f} ')) %>% 
  hc_title(
    text='Projects Sub-Counties Production',
    style = list(fontWeight = "bold", fontSize = "15px"),
    align = "center") %>% 
  hc_tooltip(sort = TRUE, table = TRUE) %>% 
  hc_add_theme(hc_theme_economist())%>% 
  hc_yAxis(title=list(text='Production (m3/d)' )) %>% 
  hc_xAxis(title=list(text='Nakuru Sub-Counties'))
 
```

Row {data-height=400}
--------------------------------------------------------------------

### Boreholes Currently Under Production

```{r}

Data4 %>% 
  group_by(Operational_Status)%>%
  summarise(Number=n())%>% 
  #arrange(-Number) %>% # indicate - to arrange from big to small
  hchart(
    'pie', hcaes(x=Operational_Status, y=Number),
    showInLegend=F,
    maxSize = "25%",
    dataLabels = list(enabled = T, format = '{point.name} , {point.y: .0f} ')) %>% 
  hc_title(
    text='Operational Status',
    style = list(fontWeight = "bold", fontSize = "15px"),
    align = "center") %>% 
  hc_tooltip(sort = TRUE, table = TRUE) %>% 
  hc_add_theme(hc_theme_538()) %>% 
  hc_yAxis(title=list(text='Number')) %>% 
  hc_xAxis(title=list(text='Operational Status'))
```

Row {data-height=600}
--------------------------------------------------------------------

### Connected Population

```{r}


Data4 %>% 
  group_by(Sub_Counties)%>%
  summarise(Households_Connected=sum(Connected_Households))%>%
  arrange(-Households_Connected)%>%# indicate - to arrange from big to small
  hchart(
    'column', hcaes(x=Sub_Counties, y= Households_Connected),
    showInLegend=F,
    maxSize = "25%",
    dataLabels = list(enabled = T, format = '{point.y: .0f} ')) %>% 
  hc_title(
    text='Household Connection Per Sub-Counties',
    style = list(fontWeight = "bold", fontSize = "15px"),
    align = "center") %>% 
  hc_tooltip(sort = TRUE, table = TRUE) %>% 
  hc_add_theme(hc_theme_darkunica())%>% 
  hc_yAxis(title=list(text='Number of Households Connected' )) %>% 
  hc_xAxis(title=list(text='Nakuru Sub-Counties'))

```

Row {data-height=400}
--------------------------------------------------------------------

### Cumulative Households Using Water Kiosk 

```{r}

Data4 %>% 
  group_by(Sub_Counties)%>%
  summarise(Households_using_Water_Kiosks=sum(Households_using_Water_Kiosks))%>%
  arrange(-Households_using_Water_Kiosks)%>%# indicate - to arrange from big to small
  hchart(
    'column', hcaes(x=Sub_Counties, y= Households_using_Water_Kiosks),
    showInLegend=F,
    maxSize = "25%",
    dataLabels = list(enabled = T, format = '{point.y: .0f} ')) %>% 
  hc_title(
    text='Household of Households Using Water Kiosks',
    style = list(fontWeight = "bold", fontSize = "15px"),
    align = "center") %>% 
  hc_tooltip(sort = TRUE, table = TRUE) %>% 
  hc_add_theme(hc_theme_flat())%>% 
  hc_yAxis(title=list(text='Number of Households using water Kiosk' )) %>% 
  hc_xAxis(title=list(text='Nakuru Sub-Counties'))


```



# {Power_Source, WRA_Permit, Collecting_Revenue & Funders }
```{r}

```



Row {data-height=400}
----------------------------------------------------------------------

### Power Source


```{r}
Data4%>%
  group_by(Power_Source)%>%
  summarise(Count=n())%>% #number of times variable appears
  e_charts(Power_Source)%>%
  e_pie(serie = Count,radius=c('30%','70%'))%>%
  e_tooltip(trigger = "item")%>%
  #e_labels(TRUE)%>%
   e_title(text = 'Operating Boreholes Power Options',
          subtext = '',
          left='center', top=20)%>%
  e_toolbox_feature('dataView')%>%
  e_toolbox_feature('restore') %>%
   e_toolbox_feature('dataZoom')%>%
  e_toolbox_feature('saveAsImage')%>%
  e_legend(orient='horizontal',left=8,top="91%")%>%
  e_theme('vintage')

```

Column {data-width=650}
----------------------------------------------------------------------

### WRA Permit

```{r}
Data4%>%
  group_by(WRA_Permit_Status)%>%
  summarise(Count=n())%>% #number of times variable appears
  e_charts(WRA_Permit_Status)%>%
  e_bar(serie = Count,radius=c('30%','70%'))%>%
  e_tooltip(trigger = "item")%>%
  #e_labels(TRUE)%>%
   e_title(text = 'WRA Permit availability Status',
          subtext = '',
          left='center', top=20)%>%
  e_toolbox_feature('dataView')%>%
  e_toolbox_feature('restore') %>%
  e_toolbox_feature('saveAsImage')%>%
  e_legend(orient='horizontal',left=8,top="90%")%>%
  e_theme('vintage')
```



### Collecting Revenue

```{r}
Data4%>%
  group_by(Revenue_Collection_Status)%>%
  summarise(Count=n())%>% #number of times variable appears
  e_charts(Revenue_Collection_Status)%>%
  e_bar(serie = Count,radius=c('30%','70%'))%>%
  e_tooltip(trigger = "item")%>%
  #e_labels(TRUE)%>%
   e_title(text = 'Collecting Revenue Status',
          subtext = '',
          left='center', top=20)%>%
  e_toolbox_feature('dataView')%>%
  e_toolbox_feature('restore') %>%
  e_toolbox_feature('saveAsImage')%>%
  e_legend(orient='horizontal',left=8,top="90%")%>%
  e_theme('dark')

```


Row {data-height=400}
----------------------------------------------------------------------

### Funders


```{r}
Data4%>%
  group_by(Funder)%>%
  summarise(Count=n())%>% #number of times variable appears
  e_charts(Funder)%>%
  e_pie(serie = Count,radius=c('30%','70%'))%>%
  e_tooltip(trigger = "item")%>%
  #e_labels(TRUE)%>%
   e_title(text = 'Primary Financial Source of the Borehole',
          subtext = '',
          left='center', top=20)%>%
  e_toolbox_feature('dataView')%>%
  e_toolbox_feature('dataZoom')%>%
  e_toolbox_feature('restore') %>%
  e_toolbox_feature('saveAsImage')%>%
  e_legend(orient='horizontal',left=8,top="85%")%>%
  e_theme('dark')

```


# (Projects Land Ownership)



```{r}

```

```{r}
Data4%>%
  group_by(Land_Owner)%>%
  summarise(Count=n())%>% #number of times variable appears
  e_charts(Land_Owner)%>%
  e_pie(serie = Count,roseType='radius')%>%
  e_tooltip(trigger = "item")%>%
  #e_labels(TRUE)%>%
   e_title(text = 'Land_Owners',
          subtext = '',
          left='center', top=10)%>%
  e_toolbox_feature('dataView')%>%
  e_toolbox_feature('restore') %>%
  e_toolbox_feature('saveAsImage')%>%
  e_legend(orient='horizontal',left=8,top="90%")%>%
  e_theme('dark')

```


# {Tables}

```{r}

```

Row {data-height=250}
----------------------------------------------------------------------

### Operational_Status


```{r}
Data4 %>% 
  group_by(Sub_Counties) %>% 
  tabyl(Sub_Counties,Operational_Status) %>% 
  adorn_totals("row") 
 # adorn_percentages("row") %>% 
  #adorn_pct_formatting()
```

Row {data-height=250}
----------------------------------------------------------------------

### WRA Permision Availability Status


```{r}
Data4 %>% 
  group_by(Sub_Counties) %>% 
  tabyl(Sub_Counties,WRA_Permit_Status) %>% 
  adorn_totals("row") 
```
Column {data-height=250}
----------------------------------------------------------------------

### Collecting  revenue Status

```{r}
Data4 %>% 
  group_by(Sub_Counties) %>% 
  tabyl(Sub_Counties,Revenue_Collection_Status) %>% 
  adorn_totals("row") 
```


Column {data-width=650}
----------------------------------------------------------------------

### Power Source

```{r}
Data4 %>% 
  group_by(Sub_Counties) %>% 
  tabyl(Sub_Counties,Power_Source) %>% 
  adorn_totals("row") %>% 
  adorn_percentages("row") %>% 
  adorn_pct_formatting()
```


# {Data}
```{r}

```




```{r}
datatable(Data4,
          caption = "Nakuru Community Boreholes Data",
          rownames = T,
          filter = "top",
          class = "hover cell-border stripe", #for making grid cells
          editable = "cell", # for editing cells
          
          extensions="Buttons",
          options = list(pageLength = 20,dom="Bfrtip", buttons=c( 'copy','csv', '' )))

```

